Building Markov State Model for a Periodically Driven Non-Equilibrium System

### 2014-08-22 writedown/period.noneq.msm/main.tex
backup

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fwd}}
\newcommand{\bwd}[0]{\textrm{bwd}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mc}[0]{\mathcal {C}}
\newcommand{\dt}[0]{\Delta t}

@@

We denote the phase space by $\Omega$, and the variable by $\vect
x$. The time-dependent probability distribution on the phase space is
denoted by $\rho(\vect x, t)$. The dynamics of the system is governed
by
\begin{align}
  \label{eqn:tmp1}
  \frac{\partial \rho(\vect x, t)}{\partial t} = \ml(t) \rho(\vect x,t),
\end{align}
where the generator $\ml(t)$ is time-dependent and assumed to be
periodic, i.e.~$\ml(t) = \ml(t+T)$, with period denoted by $T$.  Now
we discretize the phase space $\Omega$ into finite number of disjoint
sets $\{ S_1, \cdots, S_n\}$, which satisfy $\Omega = \cup_i S_i$,
$S_j\cap S_j = \emptyset,\ \forall i\neq j$.
Now the original dynamics of the system can be discretized to a time-dependent
Markov jump process:
\begin{align}
  \label{eqn:tmp2}
  \frac{d\vect p(t)}{dt} = \vect M(t)\cdot \vect p(t)
\end{align}
where
\begin{align}
  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{S_i} \rho(\vect x,t)d\vect x,
\end{align}
and the generator is approximated by finite difference scheme:
\begin{align}
  \label{eqn:tmp4}
  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in S_j \vert \vect x_{t} \in S_i) - \delta_{ij} \,]
\end{align}
From Eqn.~\eqref{eqn:tmp1} to Eqn.~\eqref{eqn:tmp2} involves several
approximations:
\begin{enumerate}
\item Eqn.~\eqref{eqn:tmp2} assumes Markovianity, which is not
  necessarily true for a reduce dynamics $\vect p(t)$.
\item Numerical error from the finite difference introduced in
  Eqn.~\eqref{eqn:tmp4}. The lag-time $\tau$ should not be too large
  to control the finite difference error, and at the same time should
  not be too small, because otherwise the statistical error would be
  large, and the Markovianity would be disturbed.
\item Although the original dynamics defined by generator $\ml(t)$ is
  periodic, the reduced one defined by $\vect M(t)$ is not necessary
  periodic, i.e.~$\vect M(t) \neq \vect M(t+T)$ in general.  In the
  simulation of biomolecules, it is reasonable, in most cases to
  assume a time-scale separation in the system. For example, the
  conformational change of the molecules is much faster than the
  covalent bond vibrations. Therefore, if the discretion $\{ S_1,
  \cdots, S_n\}$ properly captures the slow dynamics of interest, in
  the sense that within the lag-time $\tau$, the system is fully
  relaxed to a local equilibrium in the set $S_i$, then it is clear
  that the reduce system is periodic. It suggests that the lag-time
  should be right in the spectrum gap: it is shorter than the dominant
  implied timescale, and longer than the fast-relaxing time-scales.
\end{enumerate}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{fig/confs/fig-begin-1.eps}
  \caption{The Ramachandran plot presents the main conformations of the alanine dipeptide.}
  \label{fig:tmp1}
\end{figure}

At this stage we do have any analytical result regarding the quality
of approximating Eqn.~\eqref{eqn:tmp1} by
Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
numerical experiments. We have studied the alanine dipeptide system
under oscillatory EF, which was studied by
Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
and $\psi$ as slow variables. The definition of the conformations
$\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
force molecular dynamics simulation result
(i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
clarity, only the probability of conformation $\confc$ is plotted.  In
the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
20 methods present very good accuracy.  Please notice that for $M=10$,
for example, the number of discretized sets is $n=M^2=100$.  The
lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
$\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
The generator
$\vect M(t)$ is assumed to be periodic, and is estimated from the
trajectories from $t=300$ to 1000~ps.

The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
equilibrium MSM: the quality of the MSM depends on how accurate the
eigenfunctions are approximated by the discretization. The ``5 sets''
method achieve better accuracy than the uniform $M=5$ method by using
much less DOFs, because it captures the positive and negative signs of
the eigenfunctions. With larger $M$ the discretization error of the
eigenfunctions becomes smaller, so the accuracy of the MSM is improved.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob.eps}  
  \caption{The time-dependent probability of conformation
    $\confc$. The brute force MD simulation is compared with different
    discretization methods.}
  \label{fig:tmp2}
\end{figure}

@@

The Floquet theory states that for a periodic system
Eqn.~\ref{eqn:tmp2}, the solution can be written as
\begin{align}
  \label{eqn:tmp5}
  \vect p(t)  = \vect Q(t) e^{t\vect B} \vect p(0)
\end{align}
where $\vect Q(t)$ is periodic and $\vect B$ is a constant matrix.  To
analyze the spectrum, it is not difficult to infer the implied
timescales, on which the system relaxes to the periodic steady states
defined by $\vect Q(t)$.
Assume that the fundamental solution to Eqn.~\ref{eqn:tmp2} is denoted by $\boldsymbol \Phi(t)$, then
the matrix $\vect B$ can be expressed by
\begin{align}
  e^{T\vect B} = \boldsymbol \Phi^{-1}(0)\cdot \boldsymbol \Phi(T)
\end{align}
It is fully justified by choosing $ \boldsymbol \Phi(0) = I$, then
$e^{T\vect B}$ is estimated by evolving the fundamental solutions by
one period.  Calculating the eigenvalues of $e^{T\vect B}$ reveals the
implied timescales on which the non-equilibrium dynamics converges to
the periodic steady state. However, it can only resolve the processes that are longer than the period $T$.
The largest non-trivial timescales is given in table
Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.

\begin{table}
  \centering
  \caption{The first four non-trivial timescales calculated from $e^{T\vect B}$. The unit of time in the table is ps.
    $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
    in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
    the corresponding timescale is not calculated.
  }
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
    Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
    5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
    Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
    Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
    Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
    Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
    Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
    Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
    Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
    Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
    Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
    Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
    Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
    Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
    Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

@@

\section{Numerical results}
\subsection{Steady state distribution}
\begin{figure}
  \centering  
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
  \label{fig:num-1}
\end{figure}
\begin{figure}
  \centering  
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
  \label{fig:num-2}
\end{figure}

\subsection{Committors}
\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
\end{figure}

>>>>

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mc}[0]{\mathcal {C}}
\newcommand{\dt}[0]{\Delta t}

@@

We denote the phase space by $\Omega$, and the variable by $\vect
x$. The time-dependent probability distribution on the phase space is
denoted by $\rho(\vect x, t)$. The dynamics of the system is governed
by
\begin{align}
  \label{eqn:tmp1}
  \frac{\partial \rho(\vect x, t)}{\partial t} = \ml(t) \rho(\vect x,t),
\end{align}
where the generator $\ml(t)$ is time-dependent and assumed to be
periodic, i.e.~$\ml(t) = \ml(t+T)$, with period denoted by $T$.  Now
we discretize the phase space $\Omega$ into finite number of disjoint
sets $\{ S_1, \cdots, S_n\}$, which satisfy $\Omega = \cup_i S_i$,
$S_j\cap S_j = \emptyset,\ \forall i\neq j$.
Now the original dynamics of the system can be discretized to a time-dependent
Markov jump process:
\begin{align}
  \label{eqn:tmp2}
  \frac{d\vect p(t)}{dt} = \vect M(t)\cdot \vect p(t)
\end{align}
where
\begin{align}
  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{S_i} \rho(\vect x,t)d\vect x,
\end{align}
and the generator is approximated by finite difference scheme:
\begin{align}
  \label{eqn:tmp4}
  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in S_j \vert \vect x_{t} \in S_i) - \delta_{ij} \,]
\end{align}
From Eqn.~\eqref{eqn:tmp1} to Eqn.~\eqref{eqn:tmp2} involves several
approximations:
\begin{enumerate}
\item Eqn.~\eqref{eqn:tmp2} assumes Markovianity, which is not
  necessarily true for a reduce dynamics $\vect p(t)$, see e.g.~\cite{prinz2011markov}.
\item Numerical error from the finite difference introduced in
  Eqn.~\eqref{eqn:tmp4}. The lag-time $\tau$ should not be too large
  to control the finite difference error, and at the same time should
  not be too small, because otherwise the statistical error would be
  large, and the Markovianity would be disturbed.
\item Although the original dynamics defined by generator $\ml(t)$ is
  periodic, the reduced one defined by $\vect M(t)$ is not necessary
  periodic, i.e.~$\vect M(t) \neq \vect M(t+T)$ in general.  In the
  simulation of biomolecules, it is reasonable, in most cases to
  assume a time-scale separation in the system. For example, the
  conformational change of the molecules is much faster than the
  covalent bond vibrations. Therefore, if the discretion $\{ S_1,
  \cdots, S_n\}$ properly captures the slow dynamics of interest, in
  the sense that within the lag-time $\tau$, the system is fully
  relaxed to a local equilibrium in the set $S_i$, then it is clear
  that the reduce system is periodic. It suggests that the lag-time
  should be right in the spectrum gap: it is shorter than the dominant
  implied timescale, and longer than the fast-relaxing time-scales.
\end{enumerate}

\subsection{Perodicity of the reduced dynamics: investigated by alanine dipeptide under oscillatory electric field}
\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig/confs/c-2.eps}
  \caption{A schematic plot of the alanine dipeptide molecule and the dihedral angles $\phi$ and $\psi$.}
  \label{fig:tmp1}
\end{figure}

At this stage we do have any analytical result regarding the quality
of approximating Eqn.~\eqref{eqn:tmp1} by
Eqn.~\eqref{eqn:tmp2}.
It is therefore useful to investigate the discussed approximations
by a numerical example. The Markovianity of the reduce dynamics
was extensively discussed in e.g.~\cite{prinz2011markov}, so we 
will not touch this topic in the current paper. The choice of the lag-time
will be discussed later, and in this subsection we focus on the periodicity
of the reduced dynamics.
Throughout this paper, we take the alanine dipeptide system
under oscillatory EF, as an example, which was extensively studied by
Ref.~\cite{wang2014exploring}.
We choose the two dihedral angles $\phi$
and $\psi$ as slow variables (see Fig.~\ref{fig:tmp1}), and the discretization
is a uniform division of the $\phi$--$\psi$ plane. We denote the number of
division on each dihedral by $K$.

The alanine dipeptide was put into the local thermostating
environment, and was driven by a periodic electric field with period
$T = 10$~ps. The 20,000 branching trajectories started from 20,000
initial configurations that samples the equilibrium distribution.
\redc{Write a lot of details on non-equilibrium MD.}  The branching
trajectories were each 1000~ps long, and the system reaches
non-equilibrium steady state in roughly 300~ps. We compute the
generator from non-equilibrium trajectories in time interval $[t_1,
t_2]$. If the reduced dynamics were periodic, then generator $\vect
M(t)$ would not depends on the choice of the time interval. We compute
the reduced generator by two discretizations $K=2$ and $K=20$, and two
choices of time intervals $[0, 40]$ and $[320, 1000]$, and then
compare the results with the brute force result in
Fig.~\ref{fig:tmp2}. In the figure, we show the time-dependent
probability $\mathbb P\big(\phi\in[0,180), \psi\in [0,180)\big)$.
Using $K=2$ the dynamics depends on the time interval used for
calculating the generator: using time intervals $[0, 40]$ the reduced
dynamics can only reproduces the brute force result in $[0, 40]$,
while using time intervals $[0, 40]$ the reduced dynamics can only
reproduces the brute force result after 300~ps.  This shows that the
reduced dynamics is lack of periodicity.  The reason is that the
discretization is too coarse so that the dynamics cannot be fully
equilibriated within the lag-time $\tau$ in each discretized set.  For
$K=20$, the reduced dynamics does not depend on the time interval of
calculating the generator, and is consistent with the brute force
non-equilibrium simulation within the error bar. Therefore, the $K=20$
is a reliable discretization for the alanine dipeptide system.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
  \caption{The time-dependent probability $\mathbb
    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
    non-equilibrium MD simulation is compared with different
    discretization methods. The red shadow region indicates the
    statsitical uncertainty of the brute force simulation.}
  \label{fig:tmp2}
\end{figure}

\subsection{The choice of lag-time $\tau$}

As discussed before, the lag-time should be chosen a value that lies
in the spectrum gap of the original dynamics, so that it resolves the
slow dynamics, and at the same time relaxes the fast dynamics. In
practice, it is very difficult to estimate the lag-time in
priori. Therefore, we discretize the original non-equilibrium based on
different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps) and compare the
time dependent probability of $\mathbb P\big(\phi\in[0,180), \psi\in
[0,180)\big)$ estimated out of the reduced dynamics in
Fig.~\ref{fig:tmp3}.  All cases use idential discretization: $K=20$.
It is clear that when lag-time is close to the period (10~ps), the
reduced dynamics cannot resolve the probability change within a
period. However, the large lag-times are able to capture the
the overall log time behavior of the probability.
We observe no significant difference between $\tau=0.5$ and
$\tau=1.0$~ps, which means the reduced dynamics is not very sensitive
to the choice of $\tau$.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
  \caption{The time-dependent probability $\mathbb
    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
    non-equilibrium MD simulation is compared with different
    discretization methods. The red shadow region indicates the
    statsitical uncertainty of the brute force simulation.}
  \label{fig:tmp3}
\end{figure}

% The definition of the conformations
% $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
% by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
% probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
% force molecular dynamics simulation result
% (i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
% methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
% clarity, only the probability of conformation $\confc$ is plotted.  In
% the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
% 5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
% uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
% number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
% 20 methods present very good accuracy.  Please notice that for $M=10$,
% for example, the number of discretized sets is $n=M^2=100$.  The
% lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
% $\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
% The generator
% $\vect M(t)$ is assumed to be periodic, and is estimated from the
% trajectories from $t=300$ to 1000~ps.

% The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
% equilibrium MSM: the quality of the MSM depends on how accurate the
% eigenfunctions are approximated by the discretization. The ``5 sets''
% method achieve better accuracy than the uniform $M=5$ method by using
% much less DOFs, because it captures the positive and negative signs of
% the eigenfunctions. With larger $M$ the discretization error of the
% eigenfunctions becomes smaller, so the accuracy of the MSM is improved.

@@

The reduced dynamics will not provide a lot further interesting
information until we introduce the MSM to analyze the reduced dynamics. The main
difficulty is that the reduced dynamics is time-inhomogeneous, however, this can
be overcome by the Floquet theory.
The Floquet theory states that for a periodic system, e.g.~Eq.~\eqref{eqn:tmp2}, the solution can be written as
\begin{align}
  \label{eqn:tmp5}
  \vect p(t)  = \vect Q(t) e^{t\vect B} \vect p(0)
\end{align}
where $\vect Q(t)$ is periodic and $\vect B$ is a constant matrix.  To
analyze the spectrum, it is not difficult to infer the implied
timescales, on which the system relaxes to the periodic steady states
defined by $\vect Q(t)$.
Assume that the fundamental solution to Eqn.~\ref{eqn:tmp2} is denoted by $\boldsymbol \Phi(t)$, then
the matrix $\vect B$ can be expressed by
\begin{align}
  e^{T\vect B} = \boldsymbol \Phi^{-1}(0)\cdot \boldsymbol \Phi(T)
\end{align}
It is fully justified by choosing $ \boldsymbol \Phi(0) = I$, then
$e^{T\vect B}$ is estimated by evolving the fundamental solutions by
one period.
Since it is obvious that $Q(kT) = Q(0) = I,\ k\in\mathbb N$, if we only consider the state of the system
at time $kT$, then from Eq.~\eqref{eqn:tmp5} we have
\begin{align}
  \label{eqn:tmp5a}
  \vect p(kT)  = \boldsymbol\Phi^k(T) \,\vect p(0),
\end{align}
which is a time-homogeneous Markov process with transition matrix $\boldsymbol\Phi(T)$.
Please notice that in general this Markov process is not reversible.
Calculating the eigenvalues of $\boldsymbol\Phi(T)$ reveals the
implied timescales on which the non-equilibrium dynamics converges to
the periodic steady state.
The Eq.~\eqref{eqn:tmp5a} allows one to use the available techniques for time-homogeneous
Markov jump process (especially for irreversible processes)
to analyze the time-inhomogeneous dynamics Eq.~\eqref{eqn:tmp2}.
However, it can only resolve the processes that are longer than the period $T$.
Therefore, rather than going directly from Eq.~\eqref{eqn:tmp1} to Eq.~\eqref{eqn:tmp5a},
we would like to keep the intermediate step Eq.~\eqref{eqn:tmp2}.
In the following we compare the MSM with the brute force non-equilibrium simulation
by considering several properties that are of special interest.

% The largest non-trivial timescales is given in table
% Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.
% \begin{table}
%   \centering
%   \caption{The first four non-trivial timescales calculated from ${\vect B}$. The unit of time in the table is ps.
%     $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
%     in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
%     the corresponding timescale is not calculated.
%   }
%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
%     Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
%     5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
%     Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
%     Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
%     Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
%     Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
%     Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
%     Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
%     Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
%     Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
%     Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
%     Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
%     Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
%     Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
%     Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
%     \hline\hline
%   \end{tabular*}
%   \label{tab:tmp1}
% \end{table}

% \section{Numerical investigation of the accuracy of the MSM}

% At this stage we do have any analytical result regarding the quality
% of approximating Eqn.~\eqref{eqn:tmp1} by
% Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
% numerical experiments. We have studied the alanine dipeptide system
% under oscillatory EF, which was studied by
% Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
% and $\psi$ as slow variables. The discretization is the uniform division of
% the $\phi$--$\psi$ plan in to 2-dimentional bins. 
% The quality of the MSM~\eqref{eqn:tmp5a} can be checked by comparing the physical properties
% computed from the MSM and those computed by the brute force non-equilibrium molecular
% dynamics simulation from Ref.~\cite{wang2014exploring}.

\subsection{Core set identification}

\redc{Write how to detact the core sets for irreversible Markovian process}.

The coresets are denoted by $C_{R_\alpha}$, $C_\beta$ and $C_{L_\alpha}$, which correspond to
right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.

\subsection{Steady state distribution and eigenfunctions}
We investigate the steady state properties distribution at time $kT$. To make it comparible to
the free energy in equilibrium case, we take the logrithm of the properties, i.e.
\begin{align}
  \label{eq:num-tmp1}
  F_{\textrm{st}}(\phi,\psi) = \lim_{k\rightarrow\infty} -k_B\mathcal T \log p(\phi,\psi,kT),
\end{align}
where $k_B$ is the Boltzmann constant and $\mathcal T$ is the temperature of the system.
The result is given in Fig.~\ref{fig:num-1}. A good consistency between the brute force
MD simulation and the MSM is observed.

\begin{figure}
  \centering  
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
  \label{fig:num-1}
\end{figure}

% \begin{figure}
%   \centering  
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
%   \caption{The first three non-trivial eigenfunctions cdalculated by the MSM.}
%   \label{fig:num-2}
% \end{figure}

\subsection{Committors}

The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
the probability of visiting coreset $C_i$ next conditioned on being at configuration $(\phi,\psi)$.
The backward committor $q^\bwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
the probability of last coming from $C_i$  conditioned on being at configuration $(\phi,\psi)$.
For  reversible Markov processes, the forward and backward committors are identical, however, it is in general not the case
for irreversible processes. Please see Fig.~\ref{fig:num-3}--\ref{fig:num-5} for the committors.

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}
  \label{fig:num-3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
  \label{fig:num-4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
  \label{fig:num-5}
\end{figure}

@@
